Review of Assigned Readings

### 2018-01-03 paper/paper.tex
started to forumulate twitter part

\subsection{Twitter}
Outline: Growth of Social Media, Opinion Mining, Twitter -> micro-blogging platform, tweets, functionalities, etc. ; Why good for measuring opinions ?  "gold mine"; Sentiment Analysis, What we do.
Comment Severin: This part will contain the following steps and will be mostly based on Stenqvist et al. Predicting Bitcoin price fluctuation with Twitter sentiment analysis  (sections 2.2, 2.3)\\

1) Introduction sentence -> growth of social media https://www.statista.com/statistics/278414/number-of-worldwide-social-network-users/\\
2) Twitter as a "gold mine" to gather opinions -> What is twitter, Why is it valuable -> length of messages etc.\\
3) Sentiment Analysis -> what is a sentiment analysis\\
4) Sentiment Analysis of the term bitcoin based on twitter -> explain what we do \\

>>>>

\subsection{Twitter}
With the current growth of social networks, the number of global social media users reached 2.46 billion and is expected to increase to 3.02 billion by 2021 according to Statista (2018). Gabriel and Röhrs (2017) define social networks as a loose connection of people in an online or internet community respectively in a computer-based communication network (p. 12). This paper exploits the possibility to analyse shared “thoughts, views and opinions” (Stenqvist and Lönnö, 2017, p. 6) provided by such communities or communication networks.\newline
Twitter was founded in XXXX and reached XXX active users by 2017 (Twitter 2017). As a micro-blogging platform, Twitter suits the purpose of analysing investors’ interests for several reasons:
